Title Goes Here

### 2020-01-30 paper/paper.tex
This has better formatting

ghci> :t construct (,,) (rep False) (rep 3.1 :: E Double) (rep 1 :: E Int)
construct (,,) (rep False) (rep 3.1 :: E Double) (rep 1 :: E Int)
  :: E (Bool, Double, Int)
\end{lstlisting}

>>>>

ghci> :t construct (,,) (rep False) (rep 3.1 :: E Float) (rep 1 :: E Int)
construct (,,) (rep False) (rep 3.1 :: E Float) (rep 1 :: E Int)
  :: E (Bool, Float, Int)
\end{lstlisting}
